Extracting all spectra for NEON mapped stems

### 2020-09-15 R/spectral-lib.Rmd
added timer code
to see how long the spec lib code takes

```{r get-veg-data}
out_dir <- here::here("analysis","data","raw_data","spectral-lib")
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

@@

>>>>

```{r get-veg-data}
# start timer 
start_time <- Sys.time()

out_dir <- here::here("analysis","data","raw_data","spectral-lib")
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

@@

```{r how_long_did_this_take}
# stop timer
end_time <- Sys.time()

elapsed_time <- end_time - start_time

print(difftime(end_time, start_time, 
         units = c("auto", "secs", "mins", "hours",
                   "days", "weeks")))
```
